---
title: "Assignment3_LIU"
author: "LIU Jixiong"
date: "2018 11 9 "
output: html_document
---

##The homework day 3



Download, install and load some additional packages
```{r}
require(caret)
```

importing data
```{r}
Train_set <- read.table("F:/cycle ingenieur 2/semestre9/Predictive Analytics/homework/spamlearn_train.txt",header = T)
Test_set <- read.table("F:/cycle ingenieur 2/semestre9/Predictive Analytics/homework/spamlearn_test.txt",header = T)
```


The package support several metrics, for simplicity let us take classification accuracy.
Define data preprocessing options, in this case centering and scaling of variables.
```{r}
metric <- "Accuracy"
preProcess=c("center", "scale")
```

we choose 5 times repeated 2/fold CV. We also prepare a seed for random number generator to get repeatable results.

```{r}
seed <- 1
control <- trainControl(method="repeatedcv", number=2, repeats=5)
```



Initialisation of the data frame which will be used
```{r}
predictions <- data.frame(row.names =  'Accuracy')
predictions 
```

Next we train several classifiers
```{r}
warnLevel=getOption("warn")
options(warn=-1)
#CART
set.seed(seed)
fit.cart <- train(Class~., data=Train_set, method="rpart",  trControl=control)
plsClasses <- predict(fit.cart, newdata = Test_set)
CART <- confusionMatrix(data = plsClasses, Test_set$Class)
CART <- CART$overall['Accuracy']
predictions <- cbind(predictions, CART)

#LDA
set.seed(seed)
fit.lda <- train(Class~., data=Train_set, method="lda",  trControl=control)
plsClasses <- predict(fit.lda, newdata = Test_set)
LDA <- confusionMatrix(data = plsClasses, Test_set$Class)
LDA <-  LDA$overall['Accuracy']
predictions <- cbind(predictions, LDA)

#GLM
set.seed(seed)
fit.glm <- train(Class~., data=Train_set, method="glm",preProc=c("center", "scale"),  trControl=control)
plsClasses <- predict(fit.glm, newdata = Test_set)
glm <- confusionMatrix(data = plsClasses, Test_set$Class)
glm <-glm$overall['Accuracy']
predictions <- cbind(predictions, glm)

#KNN
set.seed(seed)
fit.knn <- train(Class~., data=Train_set, method="knn",preProc=c("center", "scale"),  trControl=control)
plsClasses <- predict(fit.knn, newdata = Test_set)
KNN <- confusionMatrix(data = plsClasses, Test_set$Class)
KNN<- KNN$overall['Accuracy']
predictions <- cbind(predictions, KNN)

#TREEBAG
set.seed(seed)
fit.treebag <- train(Class~., data=Train_set, method="treebag",  trControl=control)
plsClasses <- predict(fit.treebag, newdata = Test_set)
TB <- confusionMatrix(data = plsClasses, Test_set$Class)
TB<-  TB$overall['Accuracy']
predictions <- cbind(predictions, TB)

```

And finally visualization and comparison of the results of models.
```{r}
results <- resamples(list(logistic=fit.glm, knn=fit.knn,  cart=fit.cart, lda= fit.lda, treebag=fit.treebag))
bwplot(results)
```

and we have the results of the test set
```{r}
predictions 
```

which can be showed by a bar char
```{r}
predictions <- as.matrix(predictions)
barplot(predictions)
```

So acording to the result, chose the treebag model might be the best choice