---
title: "Assignment2_LIU"
author: "LIU Jixiong"
date: "2018/11/07"
output: html_document
---

##The homework day 2

Apply logistic regression and kNN algorithm to the Carseats data set, where the response variable is
discretized as High if Sales>8 and Low if Sales<=8. For both algorithms provide reliable estimates of
classification accuracy, sensitivity, specificity and Cohen’s kappa. Kappa is defined as agreement
between a given classifier and a random (majority voting) classifier. Use the following estimation
method: apply 10 fold cross-validation.


Download, install and load some additional packages
```{r}
library(ISLR)
library(caret)
require(class)
library(CORElearn)
attach(Carseats)
```


Data preprocessing 
```{r}
Value <- ifelse(Sales<8, "Low", "High")
Carseats <- data.frame(Carseats, Value)
Carseats$Sales <- NULL
head(Carseats)
```


Initialisation of the data frame which will be used
```{r}
Sales_regression = data.frame(row.names = c('Accuracy', 'Sensitivity', 'Specificity', 'Kappa'))
Sales_knn = Sales_regression
```


K folds declaration
```{r}
data <- Carseats
folds <- 10
foldIdx <- cvGen(nrow(data), k=folds)
```

Creation the models of the Logisic Regression and KNN, then save the 'Accuracy', 'Sensitivity', 'Specificity', 'Kappa' of all models into two dataframeworks, one for KNN, the other is for Logisic Regression
```{r}

# k fonds valitation
for(i in 1:folds){
  
#logistic regression
dTrain <- data[foldIdx!=i,]
dTest  <- data[foldIdx==i,]
Ture_test=Value[foldIdx==i]


glm.fit=glm(Value~.,data = dTrain,family = binomial)
glm.probs=predict(glm.fit,dTest,type="response")
glm.pred=rep("High",nrow(dTest))
glm.pred[glm.probs>.5]="Low"
ConfusionM=table(glm.pred,Ture_test)
  
ReConfusionM <- confusionMatrix(ConfusionM)
ReConfusionM <- c(ReConfusionM$overall['Accuracy'], ReConfusionM$byClass['Sensitivity'],ReConfusionM$byClass['Specificity'], ReConfusionM$overall['Kappa'])
ReConfusionM <- data.frame(ReConfusionM)

Sales_regression <- cbind(Sales_regression, ReConfusionM)

#KNN
dTrain.X=cbind(Price,CompPrice,ShelveLoc)[foldIdx!=i,]
dTest.X=cbind(Price,CompPrice,ShelveLoc)[foldIdx==i,]
High.train=Value[foldIdx!=i]
Ture_test=Value[foldIdx==i]
knn.pred=knn(dTrain.X,dTest.X, High.train, k=i)

ConfusionM=table(knn.pred,Ture_test)
ReConfusionM <- confusionMatrix(ConfusionM)
ReConfusionM <- c(ReConfusionM$overall['Accuracy'], ReConfusionM$byClass['Sensitivity'],ReConfusionM$byClass['Specificity'], ReConfusionM$overall['Kappa'])
ReConfusionM <- data.frame(ReConfusionM)

Sales_knn <- cbind(Sales_knn, ReConfusionM)

}
```


The 'Accuracy', 'Sensitivity', 'Specificity' and 'Kappa' of 10 folds for Logisic Regression
```{r}
Sales_regression
```


The 'Accuracy', 'Sensitivity', 'Specificity' and 'Kappa' of 10 folds for KNN
```{r}
Sales_knn
```

Comparate the means and the standard deviations
```{r}
cbind( transform(rowMeans(Sales_regression), SD=apply(Sales_regression,1, sd, na.rm = TRUE)),transform(rowMeans(Sales_knn), SD=apply(Sales_knn,1, sd, na.rm = TRUE)))
```

By comparing these results, it looks like logistic regression is better than KNN in this data set and it has a strong aggrement.



